Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-12 paper/galsize_paper.tex
Improved text in section 7 on Future Directions

Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering. For {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations. An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).

@@

On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy size does not leave a pure and unique signature on $\rhalf-$clustering ratios. However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models \citep{watson_conroy13}. Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal13,behroozi13_smhm,lehmann_etal15}. Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mhalo},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.

Figure \ref{fig:censatsizeratios} shows that the satellites in $\mhalo\approx10^{12}\msun$ halos can be as large as $\lesssim40-50\%$ smaller than their central galaxy counterparts. Since the satellite fraction varies quite significantly with morphology and/or color, we have demonstrated that it is entirely plausible that most of the observed environmental trends of galaxy size can be understood simply in terms of central vs. satellite size differences. The latter reflects not evolution of galaxies inside host halos, but is due to the fact that satellites have reached their peak mass at higher redshifts than the centrals. While it remains to be seen whether this explanation ends up comprising the whole story, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.

>>>>

Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering. Even for {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations. An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).

@@

On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy size does not leave a pure and unique signature on $\rhalf-$clustering ratios. However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models \citep{watson_conroy13}. Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal13,behroozi13_smhm,lehmann_etal15}. Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mhalo},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering. Because the number of free parameters required to additionally model galaxy size are so few, such analyses will be able to exploit the additional statistical leverage provided by the $\rhalf-$dependence of $\wproj(\rproj)$ to significantly improve constraints on $F_{\rm sat}(\mstar),$ without any appeal to a group-finder.

Figure \ref{fig:censatsizeratios} shows that satellites in $\mhalo\approx10^{12}\msun$ halos are $\sim25-40\%$ smaller than their central galaxy counterparts. Since the satellite fraction varies quite significantly with morphology and/or color, we have demonstrated that it is entirely plausible that most of the observed environmental trends of galaxy size can be understood simply in terms of central vs. satellite size differences. These differences are likely not driven by satellite-specific processes inside host halos, but instead are primarily due to the fact that satellites have reached their peak mass at higher redshifts than centrals. While it remains to be seen whether these statistical principles alone are sufficient to capture all the elementary trends that galaxy two-point functions exhibit with galaxy size, morphology and color, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
